Workflow and Software Documentation

### 2013-07-11 Workflow.Rnw
example of 2d plot similar to triPlot

\section{Ternary Plots}
\begin{enumerate}
\item
Plots of distributions of coefficients for the Cobb-Douglas 
with energy model can be made with \function{triPlot()} in 
file \texttt{Graphics.R}.  (Goofy labels here just to demonstrate what is possible.)
<<>>=
source("Graphics.R")
resData <- loadAllResampleData(modelType="cde", energyType="Q")
triPlot(subset(resData, method!="orig"), 
        gamma, alpha, beta,
        labels=c("gamma[1]", "alpha[2]", "sqrt(beta[3])"),
        n.grid=5,  aes_string="color=lambda", 
        size=1.7, alpha=.5 ) + 
     geom_point(data=subset(resData, method=="orig"), 
                color="red", alpha=1, size=3) +
     facet_wrap( ~ countryAbbrev ) +
     scale_colour_gradient(expression(lambda), high="navy", low="skyblue")
@
Eventually, we can build a wrapper that loads the data and builds the plot with our favorite settings.
\end{enumerate}

>>>>

\section{Ternary Plots}
\begin{enumerate}
\item
Plots of distributions of coefficients for the Cobb-Douglas 
with energy model can be made with \function{triPlot()} in 
file \texttt{Graphics.R}.  (Goofy labels here just to demonstrate what is possible.)
<<>>=
source("Graphics.R")
resData <- loadAllResampleData(modelType="cde", energyType="Q")
triPlot(subset(resData, method!="orig"), 
        gamma, alpha, beta,
        labels=c("gamma[1]", "alpha[2]", "sqrt(beta[3])"),
        n.grid=5,  aes_string="color=lambda", 
        size=1.7, alpha=.5 ) + 
     geom_point(data=subset(resData, method=="orig"), 
                color="red", alpha=1, size=3) +
     facet_wrap( ~ countryAbbrev ) +
     scale_colour_gradient(expression(lambda), high="navy", low="skyblue") 
@
Eventually, we can build a wrapper that loads the data and builds the plot with our favorite settings.

\section*{Scatterplots with two variables}

<<>>=
ggplot(data=subset(resData, method!="orig"), 
        aes(x=alpha, y=beta, color=lambda)) +
  geom_point() +
  xlab(expression(alpha)) +
  ylab(expression(beta)) +
  geom_point(data=subset(resData, method=="orig"), 
                color="red", alpha=1, size=3) +
  facet_wrap( ~ countryAbbrev ) +
  scale_colour_gradient(expression(lambda), high="navy", low="skyblue")
@
\end{enumerate}
